Probabilistic Catalogs from Crowded Star Fields

### 2012-09-13 paper/ms.tex
Started writing simulated data section

\section{MCMC Implementation}
The sampling was implemented using the Diffusive Nested Sampling \citep{dnest}
method (hereafter DNS). DNS is based on the Metropolis-Hastings algorithm and
is very generally applicable. The main difference between DNS and the standard
Metropolis-Hastings algorithm is that the target distribution is modified.
Rather than simply exploring the posterior distribution over catalog space,
DNS constructs an alternative target distribution which is a mixture of the
prior distribution with more constrained versions of the prior distribution.
The modified target distribution assists

@@

\section{Three Scenarios: Sparse, Cluster, and Crowded}
In this paper we discuss three test cases, named \sparse, \cluster
and \crowded. For the generation of the simulated
images, we used the following assumptions:

@@

\begin{figure}
\hspace{-1cm}
\includegraphics{Figures/test_cases.eps}
\end{figure}

>>>>

\section{MCMC Implementation}
The sampling was implemented using the Diffusive Nested Sampling \citep{dnest}
method (hereafter DNS). DNS is based on the Metropolis-Hastings algorithm and
is very generally applicable. The main difference between DNS and the standard
Metropolis-Hastings algorithm is that the target distribution is modified.
Rather than simply exploring the posterior distribution over catalog space,
DNS constructs an alternative target distribution which is a mixture of the
prior distribution with more constrained versions of the prior distribution.
The modified target distribution assists the sampling in several ways:
i)

@@

\section{Simulated Data}
We now apply the method to two illustrative simulated images. Each of the images
is $100 \times 100$ pixels in extent. The first image contains 100 stars and
the second image contains 1000 stars. These images are shown in
Figure~\ref{simulated_data}.

@@

\begin{figure}
\hspace{-1cm}
\includegraphics{Figures/test_cases.eps}
\caption{\label{simulated_data}}
\end{figure}
